### 2014-10-15 PrivacyProtection-2014-09-09.tex
Added %%% separators

\textbf{System Complexity vs Privacy:}
System Providers offer a service to Local Authorities, which is to provide and maintain a monitoring and mining system, e.g. for public mobility.
This system shall produce business intelligence, so that Local Authorities can improve their public services.
This task in it self has a high technical complexity and is the sole asset with financial return for System Providers.
However, this task operates on privacy sensitive data provided by monitored Citizens.
In order to ensure their privacy, System Provider would have to implement additional mechanisms, which allow Citizens to exercise control of their data.
But this will eventually raise the complexity of the monitoring and mining system.

@@

\subsubsection{Vulnerabilities}
This section outlines the vulnerabilities (Figure \ref{figure:Live+Gov Vulnerabilities}) of the proposed monitoring and mining system.
Note that vulnerabilities are not necessarily of technical nature.
The weaknesses of IT systems are often created due to misuse or misconfiguration of the various components by one or more actors.

@@

>>>>

\textbf{System Complexity vs Privacy:}
System Providers offer a service to Local Authorities, which is to provide and maintain a monitoring and mining system, e.g. for public mobility.
This system shall produce business intelligence, so that Local Authorities can improve their public services.
This task in it self has a high technical complexity and is the sole asset with financial return for System Providers.
However, this task operates on privacy sensitive data provided by monitored Citizens.
In order to ensure their privacy, System Provider would have to implement additional mechanisms, which allow Citizens to exercise control of their data.
This will not only raise the complexity of the monitoring and mining system, System Providers also have to layout the complexity in a comprehensible manner.
To effectively enable Citizens to preserve their privacy, they need to know what happens with their data.

@@

\subsubsection{Vulnerabilities}
\label{subsubsection:Vulnerabilities}
This section outlines the vulnerabilities (Figure \ref{figure:Live+Gov Vulnerabilities}) of the proposed monitoring and mining system.
Note that vulnerabilities are not necessarily of technical nature.
The weaknesses of IT systems are often created due to misuse or misconfiguration of the various components by one or more actors.

@@

\subsubsection{Threats}
This section outlines the potential threats (Figure \ref{figure:Live+Gov Threats}) for Citizen privacy in the proposed monitoring and mining System.
We derive threats from known conflicts of interests \ref{subsubsection:Conflicts of Interests} and vulnerabilities \ref{subsubsection:Vulnerabilities}
=======
\subsection{Step 2. Potential Analysis}
